Magnetized Polish doughnuts revisited

### 2017-02-24 paper.tex
small change
Adding the new figures
Added figure 6
Major work on the draft

%
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
\usepackage{hyperref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage[options]{hyperref}
% To add links in your PDF file, use the package "hyperref"
% with options according to your LaTeX or PDFLaTeX drivers.
%

@@

%   \subtitle{}

@@

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {}
  % aims heading (mandatory)
   {bla}
  % methods heading (mandatory)
   {bla}
  % results heading (mandatory)
   {bla}
  % conclusions heading (optional), leave it empty if necessary 
   {}

   \keywords{keywords here}

@@

Matter accretion on to a black hole is the most efficient form of energy production known in nature. The conversion of the
gravitational energy of the infalling matter into heat and radiation may reach efficiencies
of about 43\% in the case of rotating (Kerr) black holes. For this reason, systems formed 
by a black hole surrounded by an accretion disk are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
In particular, (geometrically) thick accretion disks are believed to be present in quasars and other active galactic nuclei, some 
X-ray binaries and microquasars, as well as in the central engine of gamma-ray bursts.

The investigation of such systems, either by analytical or numerical means, may rely on the ability to construct suitable 
representations based on physical assumptions. The construction of equilibrium models of stationary disks around black holes has a long tradition (see~\cite{Abramowicz:2013} and references therein). In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter  
 orbiting around a Kerr black hole. This fully relativistic model assumes that the disk is non-magnetized and that the matter obeys a  constant specific angular momentum distribution. This method was extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic 
 field to build magnetized tori around rotating black holes. Assuming different distributions of angular momentum in the disks, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion disks in dynamical equilibria, restricted to the purely hydrodynamical case. Building on this work, we discuss here the extension of the
models of~\citet{Qian:2009} to disks endowed with a purely toroidal magnetic field. For the particular case of constant angular momentum distributions our method shows good agreement with the results of~\citet{Komissarov:2006}.

The organization of the paper is as follows:
We assume that the test-fluid approximation holds, neglecting the self-gravity of the fluid, and assume that the space-time is described by the Kerr metric. We use geometrized units where $G = c = 1$.

%%%%%%%%%%%
\section{Framework}
%%%%%%%%%%%

Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric. In all the derivations presented below, the Kerr metric is implicitely written using standard Boyer-Lindquist coordinates. It is convenient to introduce a number of relevant characteristic radii, such as the radius
of the marginally stable circular orbit, $r_{\rm ms}$, and the radius of the marginally bound circular orbit, $r_{\rm mb}$, given by
\begin{eqnarray}
r_{\rm ms} &=& M\,\left(3+Z_2-\left[(3-Z_1)(3+Z_1+2Z_2)\right]^{1/2})\right)\,,
\\
r_{\rm mb} &=& 2M\,\left(  1-\frac{a_*}{2} + \sqrt{1-a_*} \right)\,,
\end{eqnarray}
where $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass.

@@

We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
\begin{equation}
l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
\end{equation}
where $u^{\mu}$ is the fluid four-velocity.
%
%\footnote{In Kerr-Schild coordinates. Although the use of the Boyer-Lindquist coordinates yields exactly the same mathematical derivation and results.}.
%
The relationship between $l$ and $\Omega$ is given by the equations
\begin{equation}
l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
\end{equation}
where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, i.e. the four-velocity can be written as
\begin{equation}
u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
\end{equation}
We also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$. 
\begin{equation}\label{eq:kepler}
l_{\mathrm{K}}(r) = \frac{M^{1/2}(r^{2}-2aM^{1/2}r^{1/2}+a^{2})}{r^{3/2}-2Mr^{1/2}+aM^{1/2}}\,.
\end{equation}

\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two cases, $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$. Following \citet{Qian:2009} we assume an angular momentum distribution ansatz given by  
\begin{equation}
l (r,\theta) = \left\{ \label{eq:ansatz} 
  \begin{array}{lr}
    l_0 \left(\frac{l_{\mathrm{K}}(r)}{l_0}\right)^{\beta}\sin^{2\gamma}{\theta} &  \text{for } r \geq r_{\mathrm{ms}}\\
    l_{\mathrm{ms}}(r)\sin^{2\gamma}{\theta} & \text{for } r < r_{\mathrm{ms}}
  \end{array}
\right.
\end{equation}
where constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$. Therefore, the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$, whose range of variation is given by~\citep{Qian:2009}
\begin{equation}
0 \leq \beta \leq 1, \quad -1 \leq \gamma \leq 1, \quad 1 \leq \eta \leq \eta_{\mathrm{max}},
\end{equation}
with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$. In this paper we choose $\eta = \eta_{\mathrm{max}}$, then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$. We take this choice because [explicar que esta eleccion hace que el momento angular esté comprendido entre lmb y lms para variaciones de beta entre 0 y 1. Además los discos de momento angular constante que empiezan en el cusp, no tienen borde externo para l = lmb]

@@

The equations of ideal general relativistic MHD are $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
%\begin{equation}\label{eq:e-m_cons}
%\nabla_{\mu} T^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:cons_faraday}
%\nabla_{\mu} \ast F^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:continuity}
%\nabla_{\mu} (\rho u^{\mu}) = 0,
%\end{equation}
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (w + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetized perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
Moreover,
%\begin{equation}
$^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$
%\end{equation}
is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
To integrate Eq.~\eqref{eq:diff_ver} we first assume a barotropic equation of state $w = w(p)$ of the form
\begin{equation}\label{eq:eos_fluid}
p = K w^{\kappa},
\end{equation}
with $K$ and $\kappa$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analog equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\eta},
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\eta-1} w^{\eta},
\end{equation}
where $K_{\mathrm{m}}$ and $\eta$ are constants.
This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.

Integrating Eq.~\eqref{eq:diff_ver} we obtain
\begin{equation}\label{eq:pre_full_int}
\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
\end{equation}
On the surface of the disk, and particularly on its inner edge, the conditions
$p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
are satisfied and, therefore, the integration constant is simply given by
\begin{equation}
\mathrm{const.} = \ln |u_t| - \int^l_{l_\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}\,.
\end{equation}
We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion as
\begin{equation}\label{eq:potential}
W - W_{\mathrm{in}} = \ln|u_t| - \ln|u_{t,\mathrm{in}}| - \int^{l}_{l_{\mathrm{in}}} \frac{\Omega \mathrm{d}l}{1 - \Omega l},
\end{equation}
where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
\begin{equation}\label{eq:full_int}
W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
\end{equation}
which for a barotropic equation of state can be easily integrated to give
\begin{equation}\label{eq:pre_enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\eta}{\eta - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
\end{equation}
Replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}, the previous equation reduces to
\begin{equation}\label{eq:enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\eta}{\eta - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\eta - 1} = 0,
\end{equation}
which relates the distribution of potential with the distribution of enthalpy.

%Finally, we assume a polytropic equation of state given by
%\begin{equation}\label{eq:density_eq}
%p = K \rho^{\kappa}
%\end{equation}
%where $\rho$ is the fluid density.

%%%%%%%%%%%%
\section{Methodology}
%%%%%%%%%%%%

\subsection{Building the disk}

To construct the disks we follow the approach described in \citet{Qian:2009}. First, we find the radial location of the cusp and the center of the disk in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
\begin{equation}\label{eq:radial_der_pot}
\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\,,
\end{equation}
and
\begin{equation}\label{eq:polar_der_pot}
\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\,.
\end{equation}
Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of the potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
\begin{equation}\label{eq:equatorial_pot}
W_{\mathrm{eq}}(r) = \int^{r}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
\end{equation}
Following \citet{Qian:2009} we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
\begin{equation}\label{eq:F}
F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}\,,
\end{equation}
which is an ordinary differential equation that can be integrated to obtain the location of the equipotential surfaces.

>>>>

\usepackage{graphicx}
\usepackage{txfonts}
\usepackage{hyperref}
\usepackage{color}
\usepackage{float}

\newcommand{\tf}[1]{\textcolor{red}{TF: #1}}

@@

@@

  \abstract
{We discuss new sequences of magnetized, equilibrium tori around Kerr black holes by combining two approaches previously considered in the literature. Our approach assumes that the test-fluid approximation holds, hence we neglect the self-gravity of the fluid. The models are built assuming a particular form of the angular momentum distribution from which the location and morphology of surfaces of equal pressure can be computed. This ansatz includes the  constant angular momentum case originally employed in the construction of thick tori - or Polish doughnuts - and has already been used to build equilibrium sequences of purely hydrodynamical models. We discuss the properties of the new models and their dependence on the initial parameters. These new sequences can be used as initial data for magnetohydrodynamical evolutions in general relativity.}

   \keywords{\tf{Complete keywords}}

@@

Matter accretion on to black holes is the most efficient form of energy production known in nature. The conversion of the
gravitational energy of the infalling matter into heat and radiation may reach efficiencies of about 43\% in the case of maximally rotating (Kerr) black holes. For this reason, systems formed by a black hole surrounded by an accretion disk are deemed responsible for many of the most energetic astronomical phenomena observed in the cosmos.
In particular, (geometrically) thick accretion disks (or tori) are believed to be present in quasars and other active galactic nuclei, some 
X-ray binaries and microquasars, as well as in the central engine of gamma-ray bursts.
The latter are alluded to in connection with mergers of neutron star binaries and black hole neutron star binaries, as well as with the rotational collapse that ensues at the end of the life of some massive stars. As numerical simulations show, such events  often result in a black hole surrounded by a torus.
\tf{We need to include a few references in this paragraph.}

The investigation of this type of systems, either by analytical or numerical means, may rely on the ability to construct suitable 
representations based on physical assumptions. The construction of equilibrium models of stationary disks around black holes has indeed a long tradition (see~\cite{Abramowicz:2013} and references therein). In particular, the so-called ``Polish doughnuts"~\citep{Abramowicz:1978,Kozlowski:1978} provide a  very general method to build equilibrium configurations of perfect fluid matter  
 orbiting around a Kerr black hole. This fully relativistic model assumes that the disk is non-magnetized and that the matter obeys a  constant specific angular momentum distribution. This method was later extended by~\cite{Komissarov:2006}  by adding a purely azimuthal magnetic 
 field to build magnetized tori around rotating black holes. On the other hand, assuming different distributions of angular momentum in the disks, \citet{Qian:2009} presented a method to build sequences of black hole thick accretion disks in dynamical equilibria, restricted however to the purely hydrodynamical case.

 In this paper we combine the two approaches considered in~\cite{Komissarov:2006} and~\citet{Qian:2009} to build new sequences of equilibrium tori around Kerr black holes.
 Building on those works, we present here the extension of the models of~\citet{Qian:2009} to account for disks endowed with a purely toroidal magnetic field. In our procedure we hence assume a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology
of surfaces of equal pressure can be numerically computed. As we shall show below, for the particular case of constant angular momentum distributions, our method is in good agreement with the results of~\citet{Komissarov:2006}.

The organization of the paper is as follows: Section~\ref{framework} presents the analytic framework to build the disks while Section~\ref{methodology} explains the corresponding numerical procedure. The sequences of models are discussed in Section~\ref{results}. Finally, the conclusions are summarized in Section~\ref{conclusions}, where we also briefly indicate potential extensions of this work we plan to inspect. In our work we assume that the test-fluid approximation holds, thus neglecting the self-gravity of the fluid, and further assume that the spacetime is described by the Kerr metric. We use geometrized units where $G = c = 1$.

%%%%%%%%%%%
\section{Framework}
\label{framework}
%%%%%%%%%%%

Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric. In all the derivations presented below, the Kerr metric is implicitely written using standard Boyer-Lindquist coordinates. It is convenient to introduce a number of relevant characteristic radii, such as the radius
of the marginally stable circular orbit, $r_{\rm ms}$, and the radius of the marginally bound circular orbit, $r_{\rm mb}$, given by
\begin{eqnarray}
r_{\rm ms} &=& M\,\left(3+Z_2-\left[(3-Z_1)(3+Z_1+2Z_2)\right]^{1/2})\right)\,,
\\
r_{\rm mb} &=& 2M\,\left(  1-\frac{a_*}{2} + \sqrt{1-a_*} \right)\,,
\end{eqnarray}
where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass. \tf{Check that the above expressions are correct.}

@@

We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
\begin{equation}
l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
\end{equation}
where $u^{\mu}$ is the fluid four-velocity.
The relationship between $l$ and $\Omega$ is given by the equations
\begin{equation}
l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
\end{equation}
where $g_{\mu\nu}$ is the metric tensor and we are assuming circular motion, i.e. the four-velocity can be written as
\begin{equation}
u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
\end{equation}
We also introduce the Keplerian angular momentum (for prograde motion) in the equatorial plane $l_{\mathrm{K}}$. 
\begin{equation}\label{eq:kepler}
l_{\mathrm{K}}(r) = \frac{M^{1/2}(r^{2}-2aM^{1/2}r^{1/2}+a^{2})}{r^{3/2}-2Mr^{1/2}+aM^{1/2}}\,.
\end{equation}

\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two cases, $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$. Following \citet{Qian:2009} we assume an angular momentum distribution ansatz given by  
\begin{equation}
l (r,\theta) = \left\{ \label{eq:ansatz} 
  \begin{array}{lr}
    l_0 \left(\frac{l_{\mathrm{K}}(r)}{l_0}\right)^{\beta}\sin^{2\gamma}{\theta} &  \text{for } r \geq r_{\mathrm{ms}}\\
    l_{\mathrm{ms}}(r)\sin^{2\gamma}{\theta} & \text{for } r < r_{\mathrm{ms}}
  \end{array}
\right.
\end{equation}
where constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$. Therefore, the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$, whose range of variation is given by~\citep{Qian:2009}
\begin{equation}
0 \leq \beta \leq 1, \quad -1 \leq \gamma \leq 1, \quad 1 \leq \eta \leq \eta_{\mathrm{max}},
\end{equation}
with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$. In this paper, and as it is done in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$. We take this choice because [explicar que esta eleccion hace que el momento angular esté comprendido entre lmb y lms para variaciones de beta entre 0 y 1. Además los discos de momento angular constante que empiezan en el cusp, no tienen borde externo para l = lmb] \tf{Write the explanation in the draft.}

@@

The equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
%\begin{equation}\label{eq:e-m_cons}
%\nabla_{\mu} T^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:cons_faraday}
%\nabla_{\mu} \ast F^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:continuity}
%\nabla_{\mu} (\rho u^{\mu}) = 0,
%\end{equation}
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (w + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetized perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
Moreover,
%\begin{equation}
$^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$
%\end{equation}
is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
To integrate Eq.~\eqref{eq:diff_ver} we first assume a barotropic equation of state $w = w(p)$ of the form
\begin{equation}\label{eq:eos_fluid}
p = K w^{\kappa},
\end{equation}
with $K$ and $\kappa$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analog equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\eta},
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\eta-1} w^{\eta},
\end{equation}
where $K_{\mathrm{m}}$ and $\eta$ are constants. \tf{I think we should use a different letter for the exponent instead of $\eta$ as it can be confused with the $\eta$ in the angular momentum ansatz.}
This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.

Integrating Eq.~\eqref{eq:diff_ver} we obtain
\begin{equation}\label{eq:pre_full_int}
\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
\end{equation}
On the surface of the disk, and particularly on its inner edge, the conditions
$p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
are satisfied and, therefore, the integration constant is simply given by
\begin{equation}
\mathrm{const.} = \ln |u_t| - \int^l_{l_\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}\,.
\end{equation}
We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion as
\begin{equation}\label{eq:potential}
W - W_{\mathrm{in}} = \ln|u_t| - \ln|u_{t,\mathrm{in}}| - \int^{l}_{l_{\mathrm{in}}} \frac{\Omega \mathrm{d}l}{1 - \Omega l},
\end{equation}
where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
\begin{equation}\label{eq:full_int}
W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
\end{equation}
which for a barotropic equation of state can be easily integrated to give
\begin{equation}\label{eq:pre_enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\eta}{\eta - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
\end{equation}
Replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}, the previous equation reduces to
\begin{equation}\label{eq:enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\eta}{\eta - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\eta - 1} = 0,
\end{equation}
which relates the distribution of the potential with the distribution of enthalpy.

%%%%%%%%%%%%
\section{Methodology}
\label{methodology}
%%%%%%%%%%%%

\begin{figure*}[t]
\centering
\includegraphics[scale=0.16]{figures/fig1a.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.16]{figures/fig1b.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.16]{figures/fig1c.pdf}
\caption{Comparison with Komissarov's solution for a constant angular momentum model. The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
           \label{komissarov}%
 \end{figure*}

%\subsection{Building the disk}

To construct the magnetized disks we follow the approach described in \citet{Qian:2009}. First, we find the radial location of the cusp and of the centre of the disk in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
\begin{equation}\label{eq:radial_der_pot}
\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\,,
\end{equation}
and
\begin{equation}\label{eq:polar_der_pot}
\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\,.
\end{equation}
Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of the potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
\begin{equation}\label{eq:equatorial_pot}
W_{\mathrm{eq}}(r) = \int^{r}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
\end{equation}
Following \citet{Qian:2009} we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
\begin{equation}\label{eq:F}
F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}\,,
\end{equation}
which is an ordinary differential equation that can be integrated to obtain the location of the equipotential surfaces.
